Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-01-31 supCLT.tex
supCLT.tex: 1108

%---Top matter------------------------------
\begin{document}
\title
    [CLT for Super-OU processes]
    {CLT for Super-OU Processes with stable Branching}
\author
    [Y.-X. Ren, R. Song, Z. Sun and J. Zhao]
    {Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
\address
    {Yan-Xia Ren\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
\address
    {Zhenyao Sun\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{zhenyao.sun@pku.edu.cn}
\address
    {Jianjie Zhao\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{zhaojianjie@pku.edu.cn}
%\begin{abstract}
%\end{abstract}
%\subjclass[2010]{60J80, 60F05}
%\keywords{}
%\date{}
\maketitle
%---Contents-----------------------
\section{Introduction}
\subsection{Model}
    Let $d \in \mathbb N:= \{1,2,\dots\}$.
    \deleted{For each $x\in \mathbb{R}^d$, write $|x|$ for its Euclidean norm.}
    Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator $L$ such that
\begin{equation}
\label{eq: OU generator}
    Lf(x)
        = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
        \quad \added{ x\in \mathbb R^d,}
        f \in C^2(\mathbb{R}^d),
\end{equation}
    where $\sigma>0$ and $b>0$.
    Denote by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
    Let $\psi$ be a function on $\mathbb R_+:= [0,\infty)$ with
\begin{equation}\label{mechanism}
    \psi(z)
        := - \alpha z + z^{1+\beta},
        \quad z \in \mathbb R_+,
\end{equation}
        where $\alpha > 0$ and $\beta \in (0,1) $.
    Denote by $\mathcal{M}(\mathbb{R}^d)$ the space of \added{ all} finite measures on $\mathbb{R}^d$.
    For each measurable function $f$ and measure $\mu$ write $\langle f,\mu\rangle = \int f(x)\mu(dx)$.
    Put $\|\mu\|=\langle 1,\mu\rangle$.
    We say a $\mathcal{M}(\mathbb{R}^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded measurable function $f$ on $\mathbb{R}^d$, we have
\begin{equation} \label{super}
    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
        = e^{-\langle u_f(t,\cdot), \mu \rangle},
        \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
\end{equation}
        where $(t,x) \mapsto u_f(t,x)$ is the unique locally bounded positive solution to the equation
\begin{equation}\label{eq1}
        u_f(t,x) + \Pi_x \Big[ \int_0^t\psi\big(u_f(t-s, \xi_s)\big)~ds\Big]
        = \Pi_x [f(\xi_t)],
        \quad x\in \mathbb R^d, t\geq 0.
\end{equation}

    The existence of such superprocesses is well known, see \cite{EB} for instance.
    Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$.
\added{
    According to \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations}, we have
}\deleted{
    The fact $\psi(\infty)=\infty$ and $\int^{\infty}\frac{1}{\psi(z)}~dz<\infty$ implies that the probability of extinguish event $D:= \{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ is contained in $(0,1)$, which means that our superprocess is non-persistent.
    In fact,
}
\begin{equation}
\added{
    \mathbb{P}_{\mu} (\exists t\geq 0,~\text{s.t.}~\|X_t\|=0)
    = e^{-\alpha^* \|\mu\|},
}\deleted{
    \mathbb{P}_{\mu}(D)
    = \mathbb{P}_{\mu} (\lim_{t \to \infty}\|X_t\|=0 )
    = e^{-\alpha^* \|\mu\|},
}
\end{equation}
    where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
\deleted{
    See {\cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations} }for a example.
    }

    Define the \emph{Fenyman-Kac semigroup} by
\begin{equation}\label{meansemigroup}
    T^{\alpha}_t f(x)
    :=
\added{ e^{\alpha t} T_t f(x) =}
    \Pi_x [e^{\alpha t}f(\xi_t)],
    \quad x\in \mathbb{R}^d,t\geq 0, f\in \mathscr B^+(\mathbb R^d).
\end{equation}
    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(T^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}\label{eq:meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
    = \langle T_t^\alpha f, \mu \rangle,
    \quad t\geq 0, f\in \mathscr B^+(\mathbb R^d).
\end{equation}
\deleted{Notice that $T^{\alpha}_t =e^{\alpha t}T_t$ for each $t \geq 0$.}

\subsection{OU semigroup}
    In this subsection, we recall some results on the spectrum property of the OU operator $L$ from \cite{GD}.
    Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
    It is known that $\xi$ has an invariant measure
\begin{equation}
\label{invariantdensity}
    \varphi(x)dx
    =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
    \quad x\in \mathbb{R}^d.
\end{equation}
    Let $L^2(\varphi):= \left\{ h \added{ \in \mathscr B(\mathbb R^d)}: \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
\begin{equation}
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\end{equation}
    \added{ Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb N_0 := \mathbb N\cup\{0\}$.}
    For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$, let $|p| \added{ :}=\sum_{k=1}^d p_k$, $p! \added{ :}= \prod_{k= 1}^d p_k !$ and $\partial x^p \added{ :}= \prod_{k = 1}^d\partial x_k^{p_k}$.
    The Hermite polynomials are defined by
\begin{equation}
    H_p(x)
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d, p \in \mathbb{N}_0^{d}.
\end{equation}
    It is known that \added{ $(T_t)$ is a strong continuous semigroup }\deleted{ the generator $L$ of OU process $\xi$ can be viewed as an operator} on $L^2(\varphi)$ \added{ and its generator $L$ has }\deleted{ with} eigenvalues $\sigma(L)= \{-bk: k \in \mathbb N_0\}$.
    For each $k \in \mathbb N_0$, \added{denote $A_k$ the eigenspace corresponding to eigenvalue $-bk$, then}\deleted{the eigenspace $A_k$ corresponding to eigenvalue $-bk$ is}
\begin{equation}
    A_k
    = \operatorname{Span} \{\phi_p : p\in \mathbb N_0^d, |p|=k\},
\end{equation}
where
\begin{equation}\label{eigenfunction}
    \phi_p(x)
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
    \quad x\in \mathbb{R}^d, p\in \mathbb N_0^d.
\end{equation}
    It is known that
\begin{equation}\label{semigroupformula}
    T_t\phi_p(x)
    =e^{-b|p|t}\phi_p(x),
    \quad t\geq 0, x\in \mathbb{R}^d, p\in \mathbb N_0^d.
\end{equation}
    Moreover, \deleted{it is known that} $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
    That is, for each $f\in L^2(\varphi)$,
\begin{equation}\label{semicomp1}
    f
    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
    \quad \text{in~} L^2(\varphi).
\end{equation}
    Denote by
\begin{equation}\label{order}
    \kappa(f)
    :=\inf \left \{k\geq 0: \exists ~ p\in \added{ \mathbb N_0^d }\deleted{ \mathbb{Z}_+^d},{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
\end{equation}
    the order of function $f$ in $L^2(\varphi)$.
    \added{ Note that }\deleted{ Then} $ \kappa(f)\geq 0$.
    In particular, the order of any constant function is zero.

\added{
\subsection{}
    Let $(\Omega, \mathscr F)$ be a measurable space.
    Let $\mathcal F$ be a linear subspace of real valued measurable functions on $\Omega$.
\begin{defi}
\label{def: alpha-positive operator}
    We say an operator $A: \mathcal F \to \mathcal F$ is $\alpha$-scalable for some $\alpha \in \mathbb R$ if for each $\lambda \in \mathbb R$ and $h \in \mathcal F$ we have $A (\lambda h) = |\lambda|^\alpha~ Ah$.
\end{defi}

    Suppose that $\alpha, \beta \in \mathbb R$.
    Let $A_\alpha$ and $A_\beta$ be an $\alpha$-scalable and a $\beta$-scalable operator on $\mathcal F$.
    Then it is clear that $A_\alpha A_\beta$ is an $(\alpha\beta)$-scalable operator.
}
\added{
    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$ defined by
}
\deleted{
    In this paper, we consider the class of functions of ploynomial growth $\mathcal{P}$ defined by
}
\begin{equation}
    \mathcal{P}
    :=\big \{f\in \added{ \mathscr B}\deleted{ \mathcal{B}}(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
\end{equation}
    It is \added{clear} \deleted{easy to see} that $\mathcal{P} \subset L^2(\varphi)$.
    \added{ For each $f\in \mathcal {P}$, define an operator $Q$ by $Qf(x):=\sup_{t\geq 0}e^{\kappa(f)bt} |T_tf(x)|$.}
\added{
    According to \cite[Fact 1.2]{MM}, $Q$ is an $1$-scalable operator on $\mathcal P$.
}
\deleted{
    According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R_0 \in \mathcal{P}$ such that,
\begin{equation}
\label{eq:semigroupineq}
    |T_tf(x)|
    \leq e^{-\kappa(f)bt} R_0(x),
    \quad t\geq 0, x\in \mathbb R^d.
\end{equation}
}

\subsection{}
    \added{Recall $\Gamma$} \deleted{Let} the Gamma function \deleted{$\Gamma$ be} defined by
\begin{equation}
    \Gamma (x) := \int_0^\infty t^{x-1} e^{-t}dt,
    \quad x>0,
\end{equation}
and
\begin{align}
\label{eq: definition of Gamma function}
    \Gamma(x)
    := \int_0^\infty t^{x-1} \Big(e^{-t} - \sum_{k=0}^{n-1} \frac{(-t)^k}{k!}\Big) dt,
    \quad -n< x< -n+1, n\in \mathbb N.
\end{align}
    \added{ It is known that }\deleted{ Then it is elementary to verify that}
\begin{equation}
    \Gamma(x+1) = x\Gamma(x),
    \quad x>0~\text{or}~-n< x< -n+1, n\in \mathbb N.
\end{equation}

    Fix a $\beta \in (0,1)$.
    According to \cite[Theorem 3.2. \& Theorem 3.5.]{SchillingSongVondracek2010Bernstein}, we can verify that the following function:
\begin{equation}
    z
    \mapsto z^{\beta}
    := \int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}},
    \quad z\in \mathbb C_+,
\end{equation}
\begin{itemize}
\item
    is an extension of the real function $x\mapsto x^{\beta}$ on $[0,\infty)$;
\item
    is continuous \added{ on }\deleted{ in} $\mathbb C_+\added{ :=\{x+iy: x\in [0,\infty), y\in \mathbb R\}}$;
\item
    is holomorphic \added{ on }\deleted{ in} $\mathbb C_+^0\added{ := \{x+iy:x\in (0,\infty), y\in \mathbb R\}}$.
\end{itemize}
    According to Lemma \ref{lem: extension lemma for branching mechanism} in the Appendix, we can verify that the following function:
\begin{equation}
\label{eq: stable branching on C+}
    z\mapsto
    z^{1+\beta}
    := \int_0^\infty (e^{-zy}-1+zy)\frac{dy}{\Gamma(-1-\beta)y^{2+\beta}},
    \quad z\in \mathbb C_+,
\end{equation}
\begin{itemize}
\item
    is an extension of the real function $x\mapsto x^{1+\beta}$ on $[0,\infty)$;
\item
    is continuous \added{ on }\deleted{ in} $\mathbb C_+$;
\item
    is holomorphic \added{ on }\deleted{ in} $\mathbb C_+^0$.
\end{itemize}
    Moreover, according to \eqref{eq: path integration representation of h}, for any $C^1$ path \added{ $\gamma:[0,1]\to \mathbb C_+$ }\deleted{ $\gamma:[0,1]\mapsto \mathbb C_+$},
\label{eq: integration formula for 1+beta-th power of z}
    &\gamma(1)^{1+\beta} - \gamma(0)^{1+\beta}
    = \int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{ydy}{\Gamma(-1-\beta)y^{2+\beta}}
    \\&=\int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{(-1-\beta)dy}{\Gamma(-\beta)y^{1+\beta}}
    = \int_0^1 (1+\beta) \gamma(\theta)^{\beta} \gamma'(\theta)d\theta.
    This indicates that the derivative of $z\mapsto z^{1+\beta}$ is $z\mapsto (1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
\begin{lem}
\label{lem: Lip of power function}
    There is a constant $\added{ C_{\ref{lem: Lip of power function}} } \deleted{ C_0} > 0$ such that for any $z_0,z_1 \in \mathbb C_+$,
\begin{equation}
\label{eq: Lip of power function}
    |z_0^{1+\beta} - z_1^{1+\beta}|
    \leq \added{ C_{\ref{lem: Lip of power function}} }\deleted{ C_0}(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
\end{equation}
\added{
    In particular, for each $z\in \mathbb C$, we have
$
    |z^{1+\beta}|
    \leq  C_{\ref{lem: Lip of power function}} |z|^{1+\beta}.
$
}
\end{lem}
\begin{proof}
    Notice that
\label{eq: upper bound for beta power of z}
    &|z^{\beta}|
    = \Big|\int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}}\Big|
    \\&\leq \frac{1}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge (|z|y)}{y^{1+\beta}}dy
    = \frac{|z|^{\beta}}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge t}{t^{1+\beta}}dt =: c |z|^{\beta},
    \quad z\in \mathbb C_+.
    Define a path $\gamma: [0,1] \to \mathbb C_+$ such that
\[
    \gamma(\theta)
    = z_0 (1-\theta) + \theta z_1,
    \quad \theta \in [0,1].
\]
    Then, according to \eqref{eq: integration formula for 1+beta-th power of z}, we have
    |z_0^{1+\beta} - z_1^{1+\beta}|
    &\leq (1+\beta) \int_0^1 |\gamma(\theta)^{\beta}|\cdot |\gamma'(\theta)|d\theta
    \leq (1+\beta) c_0 \sup_{\theta \in [0,1]} |\gamma(\theta)|^{\beta} \cdot |z_1-z_0|

>>>>

%---Top matter------------------------------
\begin{document}
\title
    [CLT for Super-OU processes]
    {CLT for Super-OU Processes with stable Branching}
\author
    [Y.-X. Ren, R. Song, Z. Sun and J. Zhao]
    {Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
\address
    {Yan-Xia Ren\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
\address
    {Zhenyao Sun\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{zhenyao.sun@pku.edu.cn}
\address
    {Jianjie Zhao\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{zhaojianjie@pku.edu.cn}
%\begin{abstract}
%\end{abstract}
%\subjclass[2010]{60J80, 60F05}
%\keywords{}
%\date{}
\maketitle
%---Contents-----------------------
\section{Introduction}
\subsection{Model}
    Let $d \in \mathbb N:= \{1,2,\dots\}$ and
    %\deleted{For each $x\in \mathbb{R}^d$, write $|x|$ for its Euclidean norm.}
    $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator $L$ such that
\begin{equation}
\label{eq: OU generator}
    Lf(x)
        = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
        \quad  x\in \mathbb R^d,
        f \in C^2(\mathbb{R}^d),
\end{equation}
    where $\sigma>0$ and $b>0$.
    Denote by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
    Let $\psi$ be a function on $\mathbb R_+:= [0,\infty)$ with
\begin{equation}\label{mechanism}
    \psi(z)
        := - \alpha z + z^{1+\beta},
        \quad z \in \mathbb R_+,
\end{equation}
        where $\alpha > 0$ and $\beta \in (0,1) $.
    Denote by $\mathcal{M}(\mathbb{R}^d)$ the space of all finite measures on $\mathbb{R}^d$.
    For each measurable function $f$ and measure $\mu$ write $\langle f,\mu\rangle = \int f(x)\mu(dx)$.
    Put $\|\mu\|=\langle 1,\mu\rangle$.
    We say a $\mathcal{M}(\mathbb{R}^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded measurable function $f$ on $\mathbb{R}^d$, we have
\begin{equation} \label{super}
    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
        = e^{-\langle u_f(t,\cdot), \mu \rangle},
        \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
\end{equation}
        where $(t,x) \mapsto u_f(t,x)$ is the unique locally bounded positive solution to the equation
\begin{equation}\label{eq1}
        u_f(t,x) + \Pi_x \Big[ \int_0^t\psi\big(u_f(t-s, \xi_s)\big)~ds\Big]
        = \Pi_x [f(\xi_t)],
        \quad x\in \mathbb R^d, t\geq 0.
\end{equation}

    The existence of such superprocesses is well known, see \cite{EB} for instance.
    Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$.
    According to \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations}, we have
\begin{equation}
    \mathbb{P}_{\mu} (\exists t\geq 0,~\text{s.t.}~\|X_t\|=0)
    = e^{-\alpha^* \|\mu\|},
\end{equation}
    where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.

    Define the \emph{Fenyman-Kac semigroup} by
\begin{equation}\label{meansemigroup}
    T^{\alpha}_t f(x)
    :=
    e^{\alpha t} T_t f(x) =
    \Pi_x [e^{\alpha t}f(\xi_t)],
    \quad x\in \mathbb{R}^d,t\geq 0, f\in \mathscr B^+(\mathbb R^d).
\end{equation}
    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(T^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}\label{eq:meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
    = \langle T_t^\alpha f, \mu \rangle,
    \quad t\geq 0, f\in \mathscr B^+(\mathbb R^d).
\end{equation}

\subsection{OU semigroup}
    In this subsection, we recall some results on the spectrum property of the OU operator $L$ from \cite{GD}.
    Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
    It is known that $\xi$ has an invariant measure
\begin{equation}
\label{invariantdensity}
    \varphi(x)dx
    =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
    \quad x\in \mathbb{R}^d.
\end{equation}
    Let $L^2(\varphi):= \left\{ h  \in \mathscr B(\mathbb R^d): \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
\begin{equation}
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\end{equation}
     Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb N_0 := \mathbb N\cup\{0\}$.
    For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$, let $|p| \added{ :}=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
    The Hermite polynomials are defined by
\begin{equation}
    H_p(x)
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d, p \in \mathbb{N}_0^{d}.
\end{equation}
    It is known that $(T_t)$ is a strong continuous semigroup on $L^2(\varphi)$ and its generator $L$ has eigenvalues $\sigma(L)= \{-bk: k \in \mathbb N_0\}$.
    For each $k \in \mathbb N_0$, denote $A_k$ the eigenspace corresponding to eigenvalue $-bk$, then
\begin{equation}
    A_k
    = \operatorname{Span} \{\phi_p : p\in \mathbb N_0^d, |p|=k\},
\end{equation}
where
\begin{equation}\label{eigenfunction}
    \phi_p(x)
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
    \quad x\in \mathbb{R}^d, p\in \mathbb N_0^d.
\end{equation}
    It is known that
\begin{equation}\label{semigroupformula}
    T_t\phi_p(x)
    =e^{-b|p|t}\phi_p(x),
    \quad t\geq 0, x\in \mathbb{R}^d, p\in \mathbb N_0^d.
\end{equation}
    Moreover, $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
    That is, for each $f\in L^2(\varphi)$,
\begin{equation}\label{semicomp1}
    f
    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
    \quad \text{in~} L^2(\varphi).
\end{equation}
    Denote by
\begin{equation}\label{order}
    \added{\kappa_f}\deleted{\kappa(f)}
    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb N_0^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
\end{equation}
    the order of function $f$ in $L^2(\varphi)$.
    Note that $ \kappa_f\geq 0$.
    In particular, the order of any constant function is zero.

\subsection{}
    Let $(\Omega, \mathscr F)$ be a measurable space.
    Let $\mathcal F$ be a linear subspace of real valued measurable functions on $\Omega$.
\begin{defi}
\label{def: alpha-positive operator}
    We say an operator $A: \mathcal F \to \mathcal F$ is $\alpha$-scalable for some $\alpha \in \mathbb R$ if for each $\lambda \in \mathbb R$ and $h \in \mathcal F$ we have $A (\lambda h) = |\lambda|^\alpha~ Ah$.
\end{defi}

    Suppose that $\alpha, \beta \in \mathbb R$.
    Let $A_\alpha$ and $A_\beta$ be an $\alpha$-scalable and a $\beta$-scalable operator on $\mathcal F$.
    Then it is clear that $A_\alpha A_\beta$ is an $(\alpha\beta)$-scalable operator.
    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$ defined by
\begin{equation}
    \mathcal{P}
    :=\big \{f\in \mathscr B(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
\end{equation}
    It is clear that $\mathcal{P} \subset L^2(\varphi)$.
    \added{ For each $f\in \mathcal {P}$, define an operator $Q$ by $Qf(x):=\sup_{t\geq 0}e^{\kappa(f)bt} |T_tf(x)|$.}
\added{
    According to \cite[Fact 1.2]{MM}, $Q$ is an $1$-scalable operator on $\mathcal P$.
}
\deleted{
    According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R_0 \in \mathcal{P}$ such that,
\begin{equation}
\label{eq:semigroupineq}
    |T_tf(x)|
    \leq e^{-\kappa(f)bt} R_0(x),
    \quad t\geq 0, x\in \mathbb R^d.
\end{equation}
}

\subsection{}
    Recall $\Gamma$ the Gamma function be defined by
\begin{equation}
    \Gamma (x) := \int_0^\infty t^{x-1} e^{-t}dt,
    \quad x>0,
\end{equation}
and
\begin{align}
\label{eq: definition of Gamma function}
    \Gamma(x)
    := \int_0^\infty t^{x-1} \Big(e^{-t} - \sum_{k=0}^{n-1} \frac{(-t)^k}{k!}\Big) dt,
    \quad -n< x< -n+1, n\in \mathbb N.
\end{align}
    It is known that
\begin{equation}
    \Gamma(x+1) = x\Gamma(x),
    \quad x>0~\text{or}~-n< x< -n+1, n\in \mathbb N.
\end{equation}

    Fix a $\beta \in (0,1)$.
    According to \cite[Theorem 3.2. \& Theorem 3.5.]{SchillingSongVondracek2010Bernstein}, we can verify that the following function:
\begin{equation}
    z
    \mapsto z^{\beta}
    := \int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}},
    \quad z\in \mathbb C_+,
\end{equation}
\begin{itemize}
\item
    is an extension of the real function $x\mapsto x^{\beta}$ on $[0,\infty)$;
\item
    is continuous on $\mathbb C_+ :=\{x+iy: x\in [0,\infty), y\in \mathbb R\}$;
\item
    is holomorphic on $\mathbb C_+^0:= \{x+iy:x\in (0,\infty), y\in \mathbb R\}$.
\end{itemize}
    According to Lemma \ref{lem: extension lemma for branching mechanism} in the Appendix, we can verify that the following function:
\begin{equation}
\label{eq: stable branching on C+}
    z\mapsto
    z^{1+\beta}
    := \int_0^\infty (e^{-zy}-1+zy)\frac{dy}{\Gamma(-1-\beta)y^{2+\beta}},
    \quad z\in \mathbb C_+,
\end{equation}
\begin{itemize}
\item
    is an extension of the real function $x\mapsto x^{1+\beta}$ on $[0,\infty)$;
\item
    is continuous on $\mathbb C_+$;
\item
    is holomorphic on $\mathbb C_+^0$.
\end{itemize}
    Moreover, according to \eqref{eq: path integration representation of h}, for any $C^1$ path $\gamma:[0,1]\to \mathbb C_+$ ,
\begin{align}
\label{eq: integration formula for 1+beta-th power of z}
    &\gamma(1)^{1+\beta} - \gamma(0)^{1+\beta}
    = \int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{ydy}{\Gamma(-1-\beta)y^{2+\beta}}
    \\&=\int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{(-1-\beta)dy}{\Gamma(-\beta)y^{1+\beta}}
    = \int_0^1 (1+\beta) \gamma(\theta)^{\beta} \gamma'(\theta)d\theta.
\end{align}
    This indicates that the derivative of $z\mapsto z^{1+\beta}$ is $z\mapsto (1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
\begin{lem}
\label{lem: Lip of power function}
    There is a constant $C_{\ref{lem: Lip of power function}}$ such that for any $z_0,z_1 \in \mathbb C_+$,
\begin{equation}
\label{eq: Lip of power function}
    |z_0^{1+\beta} - z_1^{1+\beta}|
    \leq C_{\ref{lem: Lip of power function}}(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
\end{equation}
    In particular, for each $z\in \mathbb C$, we have
$
    |z^{1+\beta}|
    \leq  C_{\ref{lem: Lip of power function}} |z|^{1+\beta}.
$

\end{lem}
\begin{proof}
    Notice that
\begin{align}
\label{eq: upper bound for beta power of z}
    &|z^{\beta}|
    = \Big|\int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}}\Big|
    \\&\leq \frac{1}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge (|z|y)}{y^{1+\beta}}dy
    = \frac{|z|^{\beta}}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge t}{t^{1+\beta}}dt =: c |z|^{\beta},
    \quad z\in \mathbb C_+.
\end{align}
    Define a path $\gamma: [0,1] \to \mathbb C_+$ such that
\[
    \gamma(\theta)
    = z_0 (1-\theta) + \theta z_1,
    \quad \theta \in [0,1].
\]
    Then, according to \eqref{eq: integration formula for 1+beta-th power of z}, we have
\begin{align}
    |z_0^{1+\beta} - z_1^{1+\beta}|
    &\leq (1+\beta) \int_0^1 |\gamma(\theta)^{\beta}|\cdot |\gamma'(\theta)|d\theta
    \leq (1+\beta) c_0 \sup_{\theta \in [0,1]} |\gamma(\theta)|^{\beta} \cdot |z_1-z_0|
    \\&\leq (1+\beta) c_0 ( |z_1|^{\beta}+|z_0|^{\beta} ) |z_1-z_0|.
    \qedhere
\end{align}
\end{proof}
\subsection{}
    Let $X$ be the super OU-process discussed in the previous subsections.
    Its branching mechanism $\psi$ can be extended on $\mathbb C_+$ by $\psi(z) := -\alpha z + z^{1+\beta}$ for each $z\in \mathbb C_+$.
    According to the above analysis, $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0$ with derivative
\begin{equation}
\label{eq: deriavetive of the Poission part}
    \psi'(z) := -\alpha + (1+\beta)z^{\beta},
    \quad z\in \mathbb C_+.
\end{equation}
    Write $\psi_0(z) := \psi(z) + \alpha z$ and $\psi'_0(z) := \psi'(z) + \alpha$.
    For each $f\in \mathscr B(\mathbb R^d, \mathbb C_+)$ and $x\in E$, define $\Psi_0f(x) := \psi_0(x,f(x))$ and $\Psi'_0 f(x) := \psi'_0(x,f(x))$.
    For each $t\in [0,\infty), x\in \mathbb E$ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$
    (See the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ taks values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
\begin{align}
\label{eq:chareq2}
    U_tf(x)-\int_0^t T^{\alpha}_{t-s} \Psi_0(-U_sf)(x)ds
    =i T^{\alpha}_t f(x),
    \quad t\in [0,\infty), x\in E, f\in \mathcal P.
\end{align}
